Evaluation of performances

### 2020-05-03 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Optimized number of features for selected learner-filter settings across folds.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 2)
  )

>>>>

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Optimized number of features for selected learner-filter settings across folds for task HR-NRI-VI.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 2)
  )
